---
######
title: "Interactive Maps In R by Group 7"
Author: Maria Düring, Laurtis Dybdahl and Magnus Thomsen
output: html_document
date: "2024-05-24"


### GETTING STARTED WITH LEAFLET

# Try to work through down this script, observing what happens in the plotting pane.

# Review favorite backgrounds in:

# <https://leaflet-extras.github.io/leaflet-providers/preview/>

# beware that some need extra options specified

```{r}
# To install Leaflet package, run this command at your R prompt:

#install.packages("leaflet")
```

```{r}
# We will also need this widget to make pretty maps:
#install.packages("htmlwidget")
```

```{r}
# Activate the libraries
library(leaflet)
library(htmlwidgets)
```

########## Example with Markers on a map of Europe

```{r}
# First, create labels for your points
popup = c("Robin", "Jakub", "Jannes")
```

```{r}
# You create a Leaflet map with these basic steps: you need to run the whole chain of course
leaflet() %>%                                 # create a map widget by calling the library
  addProviderTiles("Esri.WorldPhysical") %>%  # add Esri World Physical map tiles
  addAwesomeMarkers(lng = c(-3, 23, 11),      # add layers, specified with longitude for 3 points
                    lat = c(52, 53, 49),      # and latitude for 3 points
                    popup = popup)            # specify labels, which will appear if you click on the point in the map
```

```{r}
### Let's look at Sydney with setView() function in Leaflet
leaflet() %>%
  addTiles() %>%                              # add default OpenStreetMap map tiles
  addProviderTiles("Esri.WorldImagery",       # add custom Esri World Physical map tiles
                   options = providerTileOptions(opacity=0.5)) %>%     # make the Esri tile transparent
  setView(lng = 151.005006, lat = -33.9767231, zoom = 10)              # set the location of the map 
```

```{r}
# Now let's refocus on Europe again
leaflet() %>% 
  addTiles() %>% 
  setView( lng = 2.34, lat = 48.85, zoom = 5 ) %>%  # let's use setView to navigate to our area
  addProviderTiles("Esri.WorldPhysical", group = "Physical") %>% 
  addProviderTiles("Esri.WorldImagery", group = "Aerial") %>% 
  addProviderTiles("MtbMap", group = "Geo") %>% 

addLayersControl(                                 # we are adding layers control to the maps
  baseGroups = c("Geo","Aerial", "Physical"),
  options = layersControlOptions(collapsed = F))
```

# click the box in topright corner in your Viewer

# to select between different background layers

########## SYDNEY HARBOUR DISPLAY WITH LAYERS

# Let's create a more complicated map

```{r}
# Set the location and zoom level
leaflet() %>% 
  setView(151.2339084, -33.85089, zoom = 13) %>%
  addTiles()  # checking I am in the right area
```

# Bring in a choice of esri background layers

```{r}
# Create a basic basemap
l_aus <- leaflet() %>%   # assign the base location to an object
  setView(151.2339084, -33.85089, zoom = 13)
l_aus
```

```{r}
# Now, prepare to select backgrounds
esri <- grep("^Esri", providers, value = TRUE)
```

```{r}
# Select backgrounds from among provider tiles. To view them the options, 
# go to https://leaflet-extras.github.io/leaflet-providers/preview/
for (provider in esri) {
  l_aus <- l_aus %>% addProviderTiles(provider, group = provider)
}
l_aus
```

```{r}
### Map of Sydney, NSW, Australia
# We make a layered map out of the components above and write it to 
# an object called AUSmap
AUSmap <- l_aus %>%
  addLayersControl(baseGroups = names(esri),
                   options = layersControlOptions(collapsed = FALSE)) %>%
  addMiniMap(tiles = esri[[1]], toggleDisplay = TRUE,
             position = "bottomright") %>%
  addMeasure(
    position = "bottomleft",
    primaryLengthUnit = "meters",
    primaryAreaUnit = "sqmeters",
    activeColor = "#3D535D",
    completedColor = "#7D4479") %>% 
  htmlwidgets::onRender("
                        function(el, x) {
                        var myMap = this;
                        myMap.on('baselayerchange',
                        function (e) {
                        myMap.minimap.changeLayer(L.tileLayer.provider(e.name));
                        })
                        }") %>% 
addControl("", position = "topright")
```

```{r}
# run this to see your product
AUSmap
```

########## SAVE THE FINAL PRODUCT

```{r}
# Save map as a html document (optional, replacement of pushing the export button)
# only works in root

saveWidget(AUSmap, "AUSmap.html", selfcontained = TRUE)

```

################################### YOUR TASK NUMBER ONE

# Task 1: Create a Danish equivalent of AUSmap with esri layers,

# but call it DANmap

```{r}
### Let's look at Denmark with setView() function in Leaflet
leaflet() %>%
  addTiles() %>%                              # add default OpenStreetMap map tiles
  addProviderTiles("Esri.WorldImagery",       # add custom Esri World Physical map tiles
                   options = providerTileOptions(opacity=0.5)) %>%     # make the Esri tile transparent
  setView(lng = 10.1400557, lat = 56.1349177, zoom = 10)              # set the location of the map

```

########## Nobelparken DISPLAY WITH LAYERS

# Let's create a more complicated map

```{r}
# Set the location and zoom level
leaflet() %>% 
  setView(10.2029623,56.1724376 , zoom = 13) %>%
  addTiles()  # checking I am in the right area
```

# Bring in a choice of esri background layers

```{r}
# Create a basic basemap
D_map <- leaflet() %>%   # assign the base location to an object
  setView(10.2029623,56.1724376 , zoom = 13)
D_map
```

```{r}
# Now, prepare to select backgrounds
esri <- grep("^Esri", providers, value = TRUE)
```

```{r}
# Select backgrounds from among provider tiles. To view them the options, 
# go to https://leaflet-extras.github.io/leaflet-providers/preview/
for (provider in esri) {
  D_map <- D_map %>% addProviderTiles(provider, group = provider)
}
D_map
```

```{r}
### Map of Nobelparken, Aarhus, Denmark
# We make a layered map out of the components above and write it to 
# an object called DANmap
DANmap <- D_map %>%
  addLayersControl(baseGroups = names(esri),
                   options = layersControlOptions(collapsed = FALSE)) %>%
  addMiniMap(tiles = esri[[1]], toggleDisplay = TRUE,
             position = "bottomright") %>%
  addMeasure(
    position = "bottomleft",
    primaryLengthUnit = "meters",
    primaryAreaUnit = "sqmeters",
    activeColor = "#3D535D",
    completedColor = "#7D4479") %>% 
  htmlwidgets::onRender("
                        function(el, x) {
                        var myMap = this;
                        myMap.on('baselayerchange',
                        function (e) {
                        myMap.minimap.changeLayer(L.tileLayer.provider(e.name));
                        })
                        }") %>% 
  addControl("", position = "topright")
```

```{r}
# run this to see your product
DANmap
```

########## SAVE THE FINAL PRODUCT

```{r}
# Save map as a html document (optional, replacement of pushing the export button)
# only works in root

saveWidget(DANmap, "DANmap.html", selfcontained = TRUE)
```

########## ADD DATA TO LEAFLET

# In this section you will manually create machine-readable spatial

# data from GoogleMaps:

### First, go to <https://bit.ly/CreateCoordinates1>

### Enter the coordinates of your favorite leisure places in Denmark

```         
  # extracting them from the URL in googlemaps, adding name and type of monument.
  # Remember to copy the coordinates as a string, as just two decimal numbers separated by comma. 
```

# Caveats: Do NOT edit the grey columns! They populate automatically!

### Second, read the sheet into R. You will need gmail login information.

```         
  # watch the console, it may ask you to authenticate or put in the number 
  # that corresponds to the account you wish to use.
```

```{r}
# Libraries
library(tidyverse)
library(googlesheets4)
library(leaflet)
```

```{r}
# Read in a CSV with the class' coordinates
places <- read.csv("CapturingCoordinates - SA2022.csv")

                     
glimpse(places)
```
#Adjusting errors
```{r}
places[13,4] <- 54.9554015
```


```{r}
places_numeric <- places %>% 
  slice(1:42) %>% 
  mutate(Longitude=as.numeric(Longitude)) %>% 
  mutate(Latitude=as.numeric(Latitude))
```


```{r}
# load the coordinates in the map and check: are any points missing? Why?
Danmap_2 <- leaflet() %>% 
  addTiles() %>% 
  addProviderTiles("Stadia.OSMBright") %>% 
  addMarkers(lng = places_numeric$Longitude, 
             lat = places_numeric$Latitude,
             popup = places_numeric$Description)
```

## Some points are missing because some of the coordinates are not written properlyy

######################################################### 

```{r}
# Task 2: Read in the googlesheet data you and your colleagues 
# populated with data into the DANmap object you created in Task 1.
DANmap_2 <- leaflet() %>% 
  addTiles() %>% 
  addMarkers(lng = places_numeric$Longitude, 
             lat = places_numeric$Latitude,
             popup = places_numeric$Description)

DANmap_2

saveWidget(DANmap_2, "DANmap_2.html", selfcontained = TRUE)
```

```{r}
# Task 3: Can you cluster the points in Leaflet? Google "clustering options in Leaflet"
DANmap_clusters <- leaflet() %>% 
  addTiles() %>% 
  addMarkers(lng = places_numeric$Longitude, 
             lat = places_numeric$Latitude,
             popup = places_numeric$Description,
             clusterOptions = markerClusterOptions())

DANmap_clusters

saveWidget(DANmap_clusters, "DANmap_clusters.html", selfcontained = TRUE)
```

# Task 4: Look at the map and consider what it is good for and what not.

#It can show which areas or regions have the highest density of fun locations. #For example it shows that Aarhus has the most leisure locations according to this class.

```{r}
# Task 5: Find out how to display notes and classifications in the map.
DANmap_notes <- leaflet() %>% 
  addTiles() %>% 
  addMarkers(lng = places_numeric$Longitude, 
             lat = places_numeric$Latitude,
             popup=paste(
               "By:",places_numeric$Placename,"<br>",
               "Type:",places_numeric$Type,"<br>",
               "Description:",places_numeric$Description),
             clusterOptions = markerClusterOptions())


DANmap_notes
saveWidget(DANmap_notes, "DANmap_notes.html", selfcontained = TRUE)
```
